cardinalR: Generating interesting high-dimensional data structures

### 2025-09-19 paper-cardinalR.Rmd
more clear about the p
Remove 0.3 value

The main function of the package is `gen_multicluster()`, which generates datasets consisting of multiple clusters with user-specified characteristics. Users can control the number of clusters (`k`), the number of points in each cluster (`n`), and the dimensionality of the space (`p`). Each cluster can take on a different geometric shape (e.g., Gaussian, cone, uniform cube), be scaled to adjust its spread, rotated in specified planes by given angles, and positioned at defined centroids (`loc`). The function ensures flexibility in cluster location and orientation, allowing users to simulate complex high-dimensional structures. An optional argument, `is_bkg`, adds background noise drawn from a multivariate normal distribution centered on the dataset’s overall mean with standard deviations matching the observed spread.

@@

@@

To simulate missing regions on the manifold, a fixed anchor point $(0, 1, 0, \ldots)$ is defined in $p\text{-}D$. All observations within a Euclidean distance of $\sqrt{0.3} \approx 0.5477$ from the anchor are removed if $\sum_{j=1}^p (X_j - a_j)^2 \leq 0.3$. This exclusion creates a hole in the manifold centered near the middle vertical region of the S-curve.

>>>>

The main function of the package is `gen_multicluster()`, which generates datasets consisting of multiple clusters with user-specified characteristics. Users can control the number of clusters (`k`), the number of points in each cluster (`n`), and the dimensionality of the space (`p`) for all the clusters. Each cluster can take on a different geometric shape (e.g., Gaussian, cone, uniform cube), be scaled to adjust its spread, rotated in specified planes by given angles, and positioned at defined centroids (`loc`). The function ensures flexibility in cluster location and orientation, allowing users to simulate complex high-dimensional structures. An optional argument, `is_bkg`, adds background noise drawn from a multivariate normal distribution centered on the dataset’s overall mean with standard deviations matching the observed spread.

@@

### Shape generators

@@

To simulate missing regions on the manifold, a fixed anchor point $(0, 1, 0, \ldots)$ is defined in $p\text{-}D$. All observations within a Euclidean distance of $\sqrt{0.3}$ from the anchor are removed if $\sum_{j=1}^p (X_j - a_j)^2 \leq 0.3$. This exclusion creates a hole in the manifold centered near the middle vertical region of the S-curve.
